Manuscript

### 2019-01-16 manuscript_analysis.Rmd

```{r}
test <- adj_signif(ccle_signif_grid_lineage, alpha = 0.05)
length(unique(test))
```

@@

# CCLE
ccle_cor_res <- ccle_data_g2p_grid %>% group_by(Drug_Gene) %>%
                    summarize(Pearson_Corr_GE = cor.test(y = AUC_zscore, x = RPKM, method = "pearson", use = "complete.obs")$estimate,
                              Pearson_Pval_GE = cor.test(y = AUC_zscore, x = RPKM, method = "pearson", use = "complete.obs")$p.value,
                              Pearson_Corr_CN = cor.test(y = AUC_zscore, x = CN, method = "pearson", use = "complete.obs")$estimate,
                              Pearson_Pval_CN = cor.test(y = AUC_zscore, x = CN, method = "pearson", use = "complete.obs")$p.value,
                              Spearman_Corr_GE = cor.test(y = AUC_zscore, x = RPKM, method = "spearman", use = "complete.obs")$estimate,
                              Spearman_Pval_GE = cor.test(y = AUC_zscore, x = RPKM, method = "spearman", use = "complete.obs")$p.value,
                              Spearman_Corr_CN = cor.test(y = AUC_zscore, x = CN, method = "spearman", use = "complete.obs")$estimate,
                              Spearman_Pval_CN = cor.test(y = AUC_zscore, x = CN, method = "spearman", use = "complete.obs")$p.value)
ccle_cor_res <- merge(g2p_druggene_tally, ccle_cor_res, by = "Drug_Gene", all.y = TRUE)
ccle_cor_res$n <- ifelse(is.na(ccle_cor_res$n), 0, ccle_cor_res$n)
ccle_cor_res$InG2P <- ifelse(ccle_cor_res$n != 0, "Yes", "No")
ccle_cor_res$Dataset <- "CCLE"
# ccle_pearson_ttest_GE <- t.test(ccle_cor_res$Pearson_Corr_GE ~ ccle_cor_res$InG2P)
# ccle_pearson_ttest_res_GE <- paste0("t(", round(ccle_pearson_ttest_GE$parameter, 0), ") = ", round(ccle_pearson_ttest_GE$statistic, 2), ", p = ", round(ccle_pearson_ttest_GE$p.value, 2))
# ccle_pearson_ttest_CN <- t.test(ccle_cor_res$Pearson_Corr_CN ~ ccle_cor_res$InG2P)
# ccle_pearson_ttest_res_CN <- paste0("t(", round(ccle_pearson_ttest_CN$parameter, 0), ") = ", round(ccle_pearson_ttest_CN$statistic, 2), ", p = ", round(ccle_pearson_ttest_CN$p.value, 2))
# ccle_spearman_ttest_GE <- t.test(ccle_cor_res$Spearman_Corr_GE ~ ccle_cor_res$InG2P)
# ccle_spearman_ttest_res_GE <- paste0("t(", round(ccle_spearman_ttest_GE$parameter, 0), ") = ", round(ccle_spearman_ttest_GE$statistic, 2), ", p = ", round(ccle_spearman_ttest_GE$p.value, 2))
# ccle_spearman_ttest_CN <- t.test(ccle_cor_res$Spearman_Corr_CN ~ ccle_cor_res$InG2P)
# ccle_spearman_ttest_res_CN <- paste0("t(", round(ccle_spearman_ttest_CN$parameter, 0), ") = ", round(ccle_spearman_ttest_CN$statistic, 2), ", p = ", formatC(ccle_spearman_ttest_CN$p.value, 2, format = "f"))

# CTRP
ctrp_cor_res <- ctrp_data_g2p_grid %>% group_by(Drug_Gene) %>%
                    summarize(Pearson_Corr_GE = cor.test(y = AUC_zscore, x = RPKM, method = "pearson", use = "complete.obs")$estimate,
                              Pearson_Pval_GE = cor.test(y = AUC_zscore, x = RPKM, method = "pearson", use = "complete.obs")$p.value,
                              Pearson_Corr_CN = cor.test(y = AUC_zscore, x = CN, method = "pearson", use = "complete.obs")$estimate,
                              Pearson_Pval_CN = cor.test(y = AUC_zscore, x = CN, method = "pearson", use = "complete.obs")$p.value,
                              Spearman_Corr_GE = cor.test(y = AUC_zscore, x = RPKM, method = "spearman", use = "complete.obs")$estimate,
                              Spearman_Pval_GE = cor.test(y = AUC_zscore, x = RPKM, method = "spearman", use = "complete.obs")$p.value,
                              Spearman_Corr_CN = cor.test(y = AUC_zscore, x = CN, method = "spearman", use = "complete.obs")$estimate,
                              Spearman_Pval_CN = cor.test(y = AUC_zscore, x = CN, method = "spearman", use = "complete.obs")$p.value)
ctrp_cor_res <- merge(g2p_druggene_tally, ctrp_cor_res, by = "Drug_Gene", all.y = TRUE)
ctrp_cor_res$n <- ifelse(is.na(ctrp_cor_res$n), 0, ctrp_cor_res$n)
ctrp_cor_res$InG2P <- ifelse(ctrp_cor_res$n != 0, "Yes", "No")
ctrp_cor_res$Dataset <- "CTRP"
# ctrp_pearson_ttest_GE <- t.test(ctrp_cor_res$Pearson_Corr_GE ~ ctrp_cor_res$InG2P)
# ctrp_pearson_ttest_res_GE <- paste0("t(", round(ctrp_pearson_ttest_GE$parameter, 0), ") = ", round(ctrp_pearson_ttest_GE$statistic, 2), ", p ", ifelse(round(ctrp_pearson_ttest_GE$p.value, 3) == 0, "< 0.001", paste0("= ", round(ctrp_pearson_ttest_GE$p.value, 3))))
# ctrp_pearson_ttest_CN <- t.test(ctrp_cor_res$Pearson_Corr_CN ~ ctrp_cor_res$InG2P)
# ctrp_pearson_ttest_res_CN <- paste0("t(", round(ctrp_pearson_ttest_CN$parameter, 0), ") = ", round(ctrp_pearson_ttest_CN$statistic, 2), ", p = ", round(ctrp_pearson_ttest_CN$p.value, 3))
# ctrp_spearman_ttest_GE <- t.test(ctrp_cor_res$Spearman_Corr_GE ~ ctrp_cor_res$InG2P)
# ctrp_spearman_ttest_res_GE <- paste0("t(", round(ctrp_spearman_ttest_GE$parameter, 0), ") = ", round(ctrp_spearman_ttest_GE$statistic, 2), ", p = ", round(ctrp_spearman_ttest_GE$p.value, 2))
# ctrp_spearman_ttest_CN <- t.test(ctrp_cor_res$Spearman_Corr_CN ~ ctrp_cor_res$InG2P)
# ctrp_spearman_ttest_res_CN <- paste0("t(", round(ctrp_spearman_ttest_CN$parameter, 0), ") = ", round(ctrp_spearman_ttest_CN$statistic, 2), ", p = ", round(ctrp_spearman_ttest_CN$p.value, 2))

# GDSC
gdsc_cor_res <- gdsc_data_g2p_grid %>% group_by(Drug_Gene) %>%
                    summarize(Pearson_Corr_GE = cor.test(y = AUC_zscore, x = RPKM, method = "pearson", use = "complete.obs")$estimate,
                              Pearson_Pval_GE = cor.test(y = AUC_zscore, x = RPKM, method = "pearson", use = "complete.obs")$p.value,
                              Pearson_Corr_CN = cor.test(y = AUC_zscore, x = CN, method = "pearson", use = "complete.obs")$estimate,
                              Pearson_Pval_CN = cor.test(y = AUC_zscore, x = CN, method = "pearson", use = "complete.obs")$p.value,
                              Spearman_Corr_GE = cor.test(y = AUC_zscore, x = RPKM, method = "spearman", use = "complete.obs")$estimate,
                              Spearman_Pval_GE = cor.test(y = AUC_zscore, x = RPKM, method = "spearman", use = "complete.obs")$p.value,
                              Spearman_Corr_CN = cor.test(y = AUC_zscore, x = CN, method = "spearman", use = "complete.obs")$estimate,
                              Spearman_Pval_CN = cor.test(y = AUC_zscore, x = CN, method = "spearman", use = "complete.obs")$p.value)
gdsc_cor_res <- merge(g2p_druggene_tally, gdsc_cor_res, by = "Drug_Gene", all.y = TRUE)
gdsc_cor_res$n <- ifelse(is.na(gdsc_cor_res$n), 0, gdsc_cor_res$n)
gdsc_cor_res$InG2P <- ifelse(gdsc_cor_res$n != 0, "Yes", "No")
gdsc_cor_res$Dataset <- "GDSC"
# gdsc_pearson_ttest_GE <- t.test(gdsc_cor_res$Pearson_Corr_GE ~ gdsc_cor_res$InG2P)
# gdsc_pearson_ttest_res_GE <- paste0("t(", round(gdsc_pearson_ttest_GE$parameter, 0), ") = ", round(gdsc_pearson_ttest_GE$statistic, 2), ", p = ", round(gdsc_pearson_ttest_GE$p.value, 3))
# gdsc_pearson_ttest_CN <- t.test(gdsc_cor_res$Pearson_Corr_CN ~ gdsc_cor_res$InG2P)
# gdsc_pearson_ttest_res_CN <- paste0("t(", round(gdsc_pearson_ttest_CN$parameter, 0), ") = ", round(gdsc_pearson_ttest_CN$statistic, 2), ", p = ", round(gdsc_pearson_ttest_CN$p.value, 3))
# gdsc_spearman_ttest_GE <- t.test(gdsc_cor_res$Spearman_Corr_GE ~ gdsc_cor_res$InG2P)
# gdsc_spearman_ttest_res_GE <- paste0("t(", round(gdsc_spearman_ttest_GE$parameter, 0), ") = ", round(gdsc_spearman_ttest_GE$statistic, 2), ", p = ", round(gdsc_spearman_ttest_GE$p.value, 2))
# gdsc_spearman_ttest_CN <- t.test(gdsc_cor_res$Spearman_Corr_CN ~ gdsc_cor_res$InG2P)
# gdsc_spearman_ttest_res_CN <- paste0("t(", round(gdsc_spearman_ttest_CN$parameter, 0), ") = ", round(gdsc_spearman_ttest_CN$statistic, 2), ", p = ", round(gdsc_spearman_ttest_CN$p.value, 2))

# All
g2p_cor <- rbind(ccle_cor_res, ctrp_cor_res, gdsc_cor_res)
g2p_cor$Pearson_GE_Abs <- abs(g2p_cor$Pearson_Corr_GE)
g2p_cor$Pearson_GE_Sign <- ifelse(sign(g2p_cor$Pearson_Corr_GE) == 1, "+", ifelse(sign(g2p_cor$Pearson_Corr_GE) == -1, "-", "0"))
g2p_cor$Pearson_CN_Abs <- abs(g2p_cor$Pearson_Corr_CN)
g2p_cor$Pearson_CN_Sign <- ifelse(sign(g2p_cor$Pearson_Corr_CN) == 1, "+", ifelse(sign(g2p_cor$Pearson_Corr_CN) == -1, "-", "0"))
g2p_cor$Spearman_GE_Abs <- abs(g2p_cor$Spearman_Corr_GE)
g2p_cor$Spearman_GE_Sign <- ifelse(sign(g2p_cor$Spearman_Corr_GE) == 1, "+", ifelse(sign(g2p_cor$Spearman_Corr_GE) == -1, "-", "0"))
g2p_cor$Spearman_CN_Abs <- abs(g2p_cor$Spearman_Corr_CN)
g2p_cor$Spearman_CN_Sign <- ifelse(sign(g2p_cor$Spearman_Corr_CN) == 1, "+", ifelse(sign(g2p_cor$Spearman_Corr_CN) == -1, "-", "0"))
# g2p_cor_text <- data.frame(Dataset = c("CCLE", "CTRP", "GDSC"),
#                                Pearson_Test_Results_GE = c(ccle_pearson_ttest_res_GE, ctrp_pearson_ttest_res_GE, gdsc_pearson_ttest_res_GE),
#                                Pearson_Test_Results_CN = c(ccle_pearson_ttest_res_CN, ctrp_pearson_ttest_res_CN, gdsc_pearson_ttest_res_CN),
#                                Spearman_Test_Results_GE = c(ccle_spearman_ttest_res_GE, ctrp_spearman_ttest_res_GE, gdsc_spearman_ttest_res_GE),
#                                Spearman_Test_Results_CN = c(ccle_spearman_ttest_res_CN, ctrp_spearman_ttest_res_CN, gdsc_spearman_ttest_res_CN))
```

@@

Venn diagram between GE and CN:
```{r}
futile.logger::flog.threshold(futile.logger::ERROR, name = "VennDiagramLogger")
crispr_venn <- venn.diagram(list("Gene Expression" = as.character(crispr_spearman_res_GE_sig$Hugo_Symbol), "Copy Number" = as.character(crispr_spearman_res_CN_sig$Hugo_Symbol)), fill = c("darkorchid4", "mediumorchid1"), lty = rep("blank", 2), alpha = c(0.5, 0.5), cat.pos = c(-2, 5), cat.cex = 1.5, cex = 1, filename = NULL)

@@

png("./plots/manuscript/crispr_venn.png")
grid.newpage()
grid.draw(crispr_venn)
dev.off()
```

@@

ccle_dgs <- as.character(ccle_signif_g2p_grid[!is.na(ccle_signif_g2p_grid$p.signif.adj),]$Drug_Gene)
ctrp_dgs <- as.character(ctrp_signif_g2p_grid[!is.na(ctrp_signif_g2p_grid$p.signif.adj),]$Drug_Gene)
gdsc_dgs <- as.character(gdsc_signif_g2p_grid[!is.na(gdsc_signif_g2p_grid$p.signif.adj),]$Drug_Gene)

drug_venn <- venn.diagram(list("CCLE" = ccle_dgs, "CTRP" = ctrp_dgs, "GDSC" = gdsc_dgs), lty = rep("blank", 3), fill = c("springgreen4", "steelblue4", "turquoise4"), alpha = c(0.5, 0.5, 0.5), cat.pos = c(-30, 50, 120), cat.dist = c(0.001, 0.02, 0.0001), cat.cex = 1.5, cex = 1, filename = NULL)
# in GDSC only
drug_venn[[7]]$label  <- paste(sort(setdiff(setdiff(gdsc_dgs, ctrp_dgs), ccle_dgs)), collapse = "\n")
# in GDSC and CTRP only
drug_venn[[8]]$label <- paste(intersect(gdsc_dgs, ctrp_dgs), collapse = "\n")
# in CTRP only
drug_venn[[9]]$label <- paste(sort(setdiff(setdiff(ctrp_dgs, gdsc_dgs), ccle_dgs)), collapse = "\n")
# in CTRP and CCLE only
drug_venn[[10]]$label <- intersect(ccle_dgs, ctrp_dgs)

png("./plots/manuscript/drugscreen_venn.png")
grid.newpage()
grid.draw(drug_venn)
dev.off()
```

@@

@@

# ggsave("./plots/manuscript/g2p_spearman_ks_res_plot.png", g2p_ks_res_plot_spearman, device = "png", dpi = 450, width = 12, height = 6, units = "in")
```

>>>>

@@

# CCLE
ccle_cor_res <- ccle_data_g2p_grid %>% group_by(Drug_Gene) %>%
                    summarize(Pearson_Corr_GE = cor.test(y = AUC_zscore, x = RPKM, method = "pearson", use = "complete.obs")$estimate,
                              Pearson_Pval_GE = cor.test(y = AUC_zscore, x = RPKM, method = "pearson", use = "complete.obs")$p.value,
                              Pearson_Corr_CN = cor.test(y = AUC_zscore, x = CN, method = "pearson", use = "complete.obs")$estimate,
                              Pearson_Pval_CN = cor.test(y = AUC_zscore, x = CN, method = "pearson", use = "complete.obs")$p.value,
                              Spearman_Corr_GE = cor.test(y = AUC_zscore, x = RPKM, method = "spearman", use = "complete.obs")$estimate,
                              Spearman_Pval_GE = cor.test(y = AUC_zscore, x = RPKM, method = "spearman", use = "complete.obs")$p.value,
                              Spearman_Corr_CN = cor.test(y = AUC_zscore, x = CN, method = "spearman", use = "complete.obs")$estimate,
                              Spearman_Pval_CN = cor.test(y = AUC_zscore, x = CN, method = "spearman", use = "complete.obs")$p.value)
ccle_cor_res <- merge(g2p_druggene_tally, ccle_cor_res, by = "Drug_Gene", all.y = TRUE)
ccle_cor_res$n <- ifelse(is.na(ccle_cor_res$n), 0, ccle_cor_res$n)
ccle_cor_res$InG2P <- ifelse(ccle_cor_res$n != 0, "Yes", "No")
ccle_cor_res$Dataset <- "CCLE"

# CTRP
ctrp_cor_res <- ctrp_data_g2p_grid %>% group_by(Drug_Gene) %>%
                    summarize(Pearson_Corr_GE = cor.test(y = AUC_zscore, x = RPKM, method = "pearson", use = "complete.obs")$estimate,
                              Pearson_Pval_GE = cor.test(y = AUC_zscore, x = RPKM, method = "pearson", use = "complete.obs")$p.value,
                              Pearson_Corr_CN = cor.test(y = AUC_zscore, x = CN, method = "pearson", use = "complete.obs")$estimate,
                              Pearson_Pval_CN = cor.test(y = AUC_zscore, x = CN, method = "pearson", use = "complete.obs")$p.value,
                              Spearman_Corr_GE = cor.test(y = AUC_zscore, x = RPKM, method = "spearman", use = "complete.obs")$estimate,
                              Spearman_Pval_GE = cor.test(y = AUC_zscore, x = RPKM, method = "spearman", use = "complete.obs")$p.value,
                              Spearman_Corr_CN = cor.test(y = AUC_zscore, x = CN, method = "spearman", use = "complete.obs")$estimate,
                              Spearman_Pval_CN = cor.test(y = AUC_zscore, x = CN, method = "spearman", use = "complete.obs")$p.value)
ctrp_cor_res <- merge(g2p_druggene_tally, ctrp_cor_res, by = "Drug_Gene", all.y = TRUE)
ctrp_cor_res$n <- ifelse(is.na(ctrp_cor_res$n), 0, ctrp_cor_res$n)
ctrp_cor_res$InG2P <- ifelse(ctrp_cor_res$n != 0, "Yes", "No")
ctrp_cor_res$Dataset <- "CTRP"

# GDSC
gdsc_cor_res <- gdsc_data_g2p_grid %>% group_by(Drug_Gene) %>%
                    summarize(Pearson_Corr_GE = cor.test(y = AUC_zscore, x = RPKM, method = "pearson", use = "complete.obs")$estimate,
                              Pearson_Pval_GE = cor.test(y = AUC_zscore, x = RPKM, method = "pearson", use = "complete.obs")$p.value,
                              Pearson_Corr_CN = cor.test(y = AUC_zscore, x = CN, method = "pearson", use = "complete.obs")$estimate,
                              Pearson_Pval_CN = cor.test(y = AUC_zscore, x = CN, method = "pearson", use = "complete.obs")$p.value,
                              Spearman_Corr_GE = cor.test(y = AUC_zscore, x = RPKM, method = "spearman", use = "complete.obs")$estimate,
                              Spearman_Pval_GE = cor.test(y = AUC_zscore, x = RPKM, method = "spearman", use = "complete.obs")$p.value,
                              Spearman_Corr_CN = cor.test(y = AUC_zscore, x = CN, method = "spearman", use = "complete.obs")$estimate,
                              Spearman_Pval_CN = cor.test(y = AUC_zscore, x = CN, method = "spearman", use = "complete.obs")$p.value)
gdsc_cor_res <- merge(g2p_druggene_tally, gdsc_cor_res, by = "Drug_Gene", all.y = TRUE)
gdsc_cor_res$n <- ifelse(is.na(gdsc_cor_res$n), 0, gdsc_cor_res$n)
gdsc_cor_res$InG2P <- ifelse(gdsc_cor_res$n != 0, "Yes", "No")
gdsc_cor_res$Dataset <- "GDSC"

# All
g2p_cor <- rbind(ccle_cor_res, ctrp_cor_res, gdsc_cor_res)
g2p_cor$Pearson_GE_Abs <- abs(g2p_cor$Pearson_Corr_GE)
g2p_cor$Pearson_GE_Sign <- ifelse(sign(g2p_cor$Pearson_Corr_GE) == 1, "+", ifelse(sign(g2p_cor$Pearson_Corr_GE) == -1, "-", "0"))
g2p_cor$Pearson_CN_Abs <- abs(g2p_cor$Pearson_Corr_CN)
g2p_cor$Pearson_CN_Sign <- ifelse(sign(g2p_cor$Pearson_Corr_CN) == 1, "+", ifelse(sign(g2p_cor$Pearson_Corr_CN) == -1, "-", "0"))
g2p_cor$Spearman_GE_Abs <- abs(g2p_cor$Spearman_Corr_GE)
g2p_cor$Spearman_GE_Sign <- ifelse(sign(g2p_cor$Spearman_Corr_GE) == 1, "+", ifelse(sign(g2p_cor$Spearman_Corr_GE) == -1, "-", "0"))
g2p_cor$Spearman_CN_Abs <- abs(g2p_cor$Spearman_Corr_CN)
g2p_cor$Spearman_CN_Sign <- ifelse(sign(g2p_cor$Spearman_Corr_CN) == 1, "+", ifelse(sign(g2p_cor$Spearman_Corr_CN) == -1, "-", "0"))
```

Deprecated: T-tests of G2P presence/absence distributions
```{r}
# ccle_pearson_ttest_GE <- t.test(ccle_cor_res$Pearson_Corr_GE ~ ccle_cor_res$InG2P)
# ccle_pearson_ttest_res_GE <- paste0("t(", round(ccle_pearson_ttest_GE$parameter, 0), ") = ", round(ccle_pearson_ttest_GE$statistic, 2), ", p = ", round(ccle_pearson_ttest_GE$p.value, 2))
# ccle_pearson_ttest_CN <- t.test(ccle_cor_res$Pearson_Corr_CN ~ ccle_cor_res$InG2P)
# ccle_pearson_ttest_res_CN <- paste0("t(", round(ccle_pearson_ttest_CN$parameter, 0), ") = ", round(ccle_pearson_ttest_CN$statistic, 2), ", p = ", round(ccle_pearson_ttest_CN$p.value, 2))
# ccle_spearman_ttest_GE <- t.test(ccle_cor_res$Spearman_Corr_GE ~ ccle_cor_res$InG2P)
# ccle_spearman_ttest_res_GE <- paste0("t(", round(ccle_spearman_ttest_GE$parameter, 0), ") = ", round(ccle_spearman_ttest_GE$statistic, 2), ", p = ", round(ccle_spearman_ttest_GE$p.value, 2))
# ccle_spearman_ttest_CN <- t.test(ccle_cor_res$Spearman_Corr_CN ~ ccle_cor_res$InG2P)
# ccle_spearman_ttest_res_CN <- paste0("t(", round(ccle_spearman_ttest_CN$parameter, 0), ") = ", round(ccle_spearman_ttest_CN$statistic, 2), ", p = ", formatC(ccle_spearman_ttest_CN$p.value, 2, format = "f"))

# ctrp_pearson_ttest_GE <- t.test(ctrp_cor_res$Pearson_Corr_GE ~ ctrp_cor_res$InG2P)
# ctrp_pearson_ttest_res_GE <- paste0("t(", round(ctrp_pearson_ttest_GE$parameter, 0), ") = ", round(ctrp_pearson_ttest_GE$statistic, 2), ", p ", ifelse(round(ctrp_pearson_ttest_GE$p.value, 3) == 0, "< 0.001", paste0("= ", round(ctrp_pearson_ttest_GE$p.value, 3))))
# ctrp_pearson_ttest_CN <- t.test(ctrp_cor_res$Pearson_Corr_CN ~ ctrp_cor_res$InG2P)
# ctrp_pearson_ttest_res_CN <- paste0("t(", round(ctrp_pearson_ttest_CN$parameter, 0), ") = ", round(ctrp_pearson_ttest_CN$statistic, 2), ", p = ", round(ctrp_pearson_ttest_CN$p.value, 3))
# ctrp_spearman_ttest_GE <- t.test(ctrp_cor_res$Spearman_Corr_GE ~ ctrp_cor_res$InG2P)
# ctrp_spearman_ttest_res_GE <- paste0("t(", round(ctrp_spearman_ttest_GE$parameter, 0), ") = ", round(ctrp_spearman_ttest_GE$statistic, 2), ", p = ", round(ctrp_spearman_ttest_GE$p.value, 2))
# ctrp_spearman_ttest_CN <- t.test(ctrp_cor_res$Spearman_Corr_CN ~ ctrp_cor_res$InG2P)
# ctrp_spearman_ttest_res_CN <- paste0("t(", round(ctrp_spearman_ttest_CN$parameter, 0), ") = ", round(ctrp_spearman_ttest_CN$statistic, 2), ", p = ", round(ctrp_spearman_ttest_CN$p.value, 2))

# gdsc_pearson_ttest_GE <- t.test(gdsc_cor_res$Pearson_Corr_GE ~ gdsc_cor_res$InG2P)
# gdsc_pearson_ttest_res_GE <- paste0("t(", round(gdsc_pearson_ttest_GE$parameter, 0), ") = ", round(gdsc_pearson_ttest_GE$statistic, 2), ", p = ", round(gdsc_pearson_ttest_GE$p.value, 3))
# gdsc_pearson_ttest_CN <- t.test(gdsc_cor_res$Pearson_Corr_CN ~ gdsc_cor_res$InG2P)
# gdsc_pearson_ttest_res_CN <- paste0("t(", round(gdsc_pearson_ttest_CN$parameter, 0), ") = ", round(gdsc_pearson_ttest_CN$statistic, 2), ", p = ", round(gdsc_pearson_ttest_CN$p.value, 3))
# gdsc_spearman_ttest_GE <- t.test(gdsc_cor_res$Spearman_Corr_GE ~ gdsc_cor_res$InG2P)
# gdsc_spearman_ttest_res_GE <- paste0("t(", round(gdsc_spearman_ttest_GE$parameter, 0), ") = ", round(gdsc_spearman_ttest_GE$statistic, 2), ", p = ", round(gdsc_spearman_ttest_GE$p.value, 2))
# gdsc_spearman_ttest_CN <- t.test(gdsc_cor_res$Spearman_Corr_CN ~ gdsc_cor_res$InG2P)
# gdsc_spearman_ttest_res_CN <- paste0("t(", round(gdsc_spearman_ttest_CN$parameter, 0), ") = ", round(gdsc_spearman_ttest_CN$statistic, 2), ", p = ", round(gdsc_spearman_ttest_CN$p.value, 2))

# g2p_cor_text <- data.frame(Dataset = c("CCLE", "CTRP", "GDSC"),
#                                Pearson_Test_Results_GE = c(ccle_pearson_ttest_res_GE, ctrp_pearson_ttest_res_GE, gdsc_pearson_ttest_res_GE),
#                                Pearson_Test_Results_CN = c(ccle_pearson_ttest_res_CN, ctrp_pearson_ttest_res_CN, gdsc_pearson_ttest_res_CN),
#                                Spearman_Test_Results_GE = c(ccle_spearman_ttest_res_GE, ctrp_spearman_ttest_res_GE, gdsc_spearman_ttest_res_GE),
#                                Spearman_Test_Results_CN = c(ccle_spearman_ttest_res_CN, ctrp_spearman_ttest_res_CN, gdsc_spearman_ttest_res_CN))
```

@@

Venn diagram between GE and CN:
```{r}
futile.logger::flog.threshold(futile.logger::ERROR, name = "VennDiagramLogger")
crispr_spearman_res_GE_sig <- filter(crispr_spearman_res_GE, p < 0.05)
crispr_spearman_res_CN_sig <- filter(crispr_spearman_res_CN, p < 0.05)
crispr_venn <- venn.diagram(list("Gene Expression" = as.character(crispr_spearman_res_GE_sig$Hugo_Symbol), "Copy Number" = as.character(crispr_spearman_res_CN_sig$Hugo_Symbol)), fill = c("darkorchid4", "mediumorchid1"), lty = rep("blank", 2), alpha = c(0.5, 0.5), cat.pos = c(-2, 5), cat.cex = 1.5, cex = 1, filename = NULL)

@@

ggsave("./plots/manuscript/crispr_venn.pdf", crispr_venn)
```

@@

@@

### Venn diagrams

ccle_mut_dgs <- as.character(ccle_signif_g2p_grid[!is.na(ccle_signif_g2p_grid$p.signif.adj),]$Drug_Gene)
ctrp_mut_dgs <- as.character(ctrp_signif_g2p_grid[!is.na(ctrp_signif_g2p_grid$p.signif.adj),]$Drug_Gene)
gdsc_mut_dgs <- as.character(gdsc_signif_g2p_grid[!is.na(gdsc_signif_g2p_grid$p.signif.adj),]$Drug_Gene)

ccle_ge_dgs <- as.character(ccle_cor_res[ccle_cor_res$Spearman_Pval_GE < 0.05,]$Drug_Gene)
ctrp_ge_dgs <- as.character(ctrp_cor_res[ctrp_cor_res$Spearman_Pval_GE < 0.05,]$Drug_Gene)
gdsc_ge_dgs <- as.character(gdsc_cor_res[gdsc_cor_res$Spearman_Pval_GE < 0.05,]$Drug_Gene)

ccle_cn_dgs <- as.character(ccle_cor_res[ccle_cor_res$Spearman_Pval_CN < 0.05,]$Drug_Gene)
ctrp_cn_dgs <- as.character(ctrp_cor_res[ctrp_cor_res$Spearman_Pval_CN < 0.05,]$Drug_Gene)
gdsc_cn_dgs <- as.character(gdsc_cor_res[gdsc_cor_res$Spearman_Pval_CN < 0.05,]$Drug_Gene)

drug_venn_mut <- venn.diagram(list("CCLE" = ccle_mut_dgs, "CTRP" = ctrp_mut_dgs, "GDSC" = gdsc_mut_dgs), resolution = 5000, main = "A", main.pos = c(0, 1), main.fontface = "bold", lty = rep("blank", 3), fill = c("springgreen4", "steelblue4", "turquoise4"), alpha = c(0.5, 0.5, 0.5), cat.pos = c(-30, 50, 120), cat.dist = c(0.001, 0.02, 0.0001), cat.cex = 1.5, cex = 1, filename = NULL, height = 4000)
# in GDSC only
drug_venn_mut[[7]]$label  <- paste(sort(setdiff(setdiff(gdsc_dgs, ctrp_dgs), ccle_dgs)), collapse = "\n")
# in GDSC and CTRP only
drug_venn_mut[[8]]$label <- paste(intersect(gdsc_dgs, ctrp_dgs), collapse = "\n")
# in CTRP only
drug_venn_mut[[9]]$label <- paste(sort(setdiff(setdiff(ctrp_dgs, gdsc_dgs), ccle_dgs)), collapse = "\n")
# in CTRP and CCLE only
drug_venn_mut[[10]]$label <- intersect(ccle_dgs, ctrp_dgs)

drug_venn_ge <- venn.diagram(list("CCLE" = ccle_ge_dgs, "CTRP" = ctrp_ge_dgs, "GDSC" = gdsc_ge_dgs), resolution = 5000, main = "B", main.pos = c(0, 1), main.fontface = "bold", lty = rep("blank", 3), fill = c("springgreen4", "steelblue4", "turquoise4"), alpha = c(0.5, 0.5, 0.5), cat.pos = c(-30, 30, 180), cat.dist = c(0.001, 0.001, 0.001), cat.cex = 1.5, cex = 1, filename = NULL)

drug_venn_cn <- venn.diagram(list("CCLE" = ccle_cn_dgs, "CTRP" = ctrp_cn_dgs, "GDSC" = gdsc_cn_dgs), resolution = 5000, main = "C", main.pos = c(0, 1), main.fontface = "bold", lty = rep("blank", 3), fill = c("springgreen4", "steelblue4", "turquoise4"), alpha = c(0.5, 0.5, 0.5), cat.pos = c(0, 0, 0), cat.dist = c(0.11, 0.11, 0.001), cat.cex = 1.5, cex = 1, filename = NULL)

grid.arrange(grobTree(drug_venn_mut),
             grobTree(drug_venn_ge),
             grobTree(drug_venn_cn),
             ncol = 1, 
             heights = c(2/5, 2/5, 1/5))

drugscreen_venns <- arrangeGrob(grobTree(drug_venn_mut),
             grobTree(drug_venn_ge),
             grobTree(drug_venn_cn),
             ncol = 1, 
             heights = c(2/5, 2/5, 1/5))
 # ggsave(file = "./plots/manuscript/drugscreen_venns.pdf", drugscreen_venns) #saves g

# png("./plots/manuscript/drugscreen_venn_mut.png")
# grid.newpage()
# grid.draw(drug_venn_mut)
# dev.off()
```

@@

# ggsave("./plots/manuscript/g2p_spearman_ks_res_plot.pdf", g2p_ks_res_plot_spearman, device = "pdf", dpi = 500, width = 12, height = 6, units = "in")
```
